### 2018-04-24 ident/docs/draft_3.tex
add figure for 3.1

	%In kinetic models of metabolic networks (Equation \ref{eq:kinstoich}), the fluxes are expressed as a function of the metabolite concentrations $x$ and the kinetic parameters $\theta$ (Figure \ref{fig:ident-flowchart}a). The value of every flux $v_i$, $i={1, 2, ..., n_r}$, is expressed using one of the many available enzyme kinetic formulations (Equation \ref{eq:output}b). Without loss of generality, all of these kinetic formulations can be expressed as nonlinear algebraic equations (Figure \ref{fig:ident-flowchart}a).

@@

	\section{Results:}
	First, in section \ref{sec:example}, we demonstrate the use of the methodology that we described in section \ref{sec:ident} to practically identify parameters in flux $v_1$ of the small gluconeogenic network (Figure \ref{fig:network}) model given in section \ref{sec:small-model}. In Section \ref{sec:proof} that follows, we show how the demonstrated methodology is capable of identifying and estimating parameters for fluxes $v_1$, $v_2$, and $v_5$ using steady state flux values and metabolite concentrations. We also discuss the ability of the proposed methodology to determine the structural and practical non-identifiability of parameters modeling $v_3$ in this section. The various ways in which this information can be used for designing experiments to generate data that can facilitate estimation of identifiable parameters are discussed in Section \ref{sec:experiment_type} that follows.

	\subsection{Identifying parameters in kinetic models of metabolism: an example}\label{sec:example}	
	\subsection{Relationship between structurally and practically parameter identifiability}\label{sec:proof}
	\subsection{Degree of identifiability of different enzyme kinetic rate laws}\label{sec:ident_rate_laws}			
	\subsection{Rationale for a priori experimental design through practical parameter identification}\label{sec:data_utility}	
	\subsection{Experimental requirements for identifying parameters depend on the position of the flux in the metabolic network}\label{sec:experiment_type}

	\subsection{Effect of noise on degree of identifiability is dependent on nonlinearity of enzyme kinetic rate law models}\label{sec:noise}

@@

	\clearpage
	\section{Tables, Figures and Figure Captions:}
	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=.9\textwidth,height=.6\textheight,keepaspectratio]{figures/figure3/ident_analysis}}
		\caption{A flow diagram showing the methodology developed to establish practical identifiability of parameters in kinetic models of metabolism. a) The steps for the construction of a kinetic model of a metabolic network. The choice of rate law formulations to describe metabolic fluxes influences the identification methodology. The identifiability of parameters for each flux can be established independently. b) The steps for practical identifiability analysis for parameters of a single flux.}\label{fig:ident-flowchart}
	\end{figure}

>>>>

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=.9\textwidth,height=.6\textheight,keepaspectratio]{figures/figure3/ident_analysis}}
		\caption{A flow diagram showing the methodology developed to establish practical identifiability of parameters in kinetic models of metabolism. a) The steps for the construction of a kinetic model of a metabolic network. The choice of rate law formulations to describe metabolic fluxes influences the identification methodology. The identifiability of parameters for each flux can be established independently. b) The steps for practical identifiability analysis for parameters of a single flux.}\label{fig:ident-flowchart}
	\end{figure}

@@

	\section{Results:}
	First, in Section \ref{sec:example}, we demonstrate the use of the methodology that we described in section 2.1 to practically identify parameters in flux v1 of the small gluconeogenic network (Figure \ref{fig:network}) model given in Section \ref{sec:small-model}. In Section 3.2 that follows, we show how the demonstrated methodology is capable of identifying and estimating parameters for fluxes $v_1$, $v_2$ and $v_5$ using steady state flux values and metabolite concentrations. We discuss the ability of the proposed methodology to determine the structural and practical non-identifiability of parameters modeling $v_3$ in Section \ref{sec:proof}. The contribution of the uncertainty in the data (due to differences between in vivo and in vitro kinetics) towards identifying parameters in enzyme kinetic models is discussed in Section \ref{sec:uncertainty}. The various ways in which this information can be used for designing experiments to generate data that can facilitate estimation of identifiable parameters are discussed in Section \ref{sec:design} that follows.

	\subsection{Identifying parameters in kinetic models of metabolism: an example}\label{sec:example}	
	In this section, we illustrate the proposed methodology step by step to identify parameters of flux $v_1$ in the small metabolic network (Figure \ref{fig:network} and Section \ref{sec:small-model} of the Supplementary Information). We choose the expression for flux $v_1$ given in Equation (\ref{eq:flux1a}) for this demonstration. 
	\begin{align}\tag{S5}
	v_1 = V_1^{max}\frac{ac}{ac+K_{1}^{ac}(ne)}
	\end{align}		
	Since $\theta = \{V_1^{max}, K_1^{ac} (ne)\} \in \mathbb{R}^2$ for $v_1$, as mentioned in Section \ref{sec:experiments}, we need steady state concentration and flux measurements from at least two different experiments. So, from the $n_E = 21$ different experiments described in Section \ref{sec:experiments} and Table \ref{tab:pval}, we can choose multiple combinations of $p = 2$ experiments to satisfy the data requirements for identifying $v_1$ i.e., in Equation (\ref{eq:nonlineq}) $j = \{1, 2\}$. We label the available concentrations and fluxes as ${ac}^{(j)}$ and ${v_1}^{(j)}$, respectively. Then, the nonlinear algebraic equations shown in Equation (\ref{eq:nonlineq}) can be formulated for $v_1$ as:
	\begin{align*}%\label{eq:nonlin-flux2}
	{v_1}^{(j)} = V_{1}^{max}\frac{ac^{(j)}}{ac^{(j)}+K_{1}^{ac}(ne)} &&  j=\{1, 2\}
	\end{align*}

	Solving this simultaneous system of equations in $\mathbb{R}^2$ using Mathematica (Wolfram Research, USA), a computer algebra system, we get $p=2$ nonlinear algebraic expressions for parameters $V_1^{max}$ (Equation \ref{eq:v1_par}a) and $K_1^{ac}(ne)$ (Equation \ref{eq:v1_par}b). These expressions have the form shown in Equation (\ref{eq:theta-eq}).
	\begin{subequations}\label{eq:v1_par}
		\begin{align}		
		\theta_1 &= V_1^{max} = \frac{v_1^{(1)}v_1^{(2)}(ac^{(1)}-ac^{(2)})}{v_1^{(2)}ac^{(1)}-v_1^{(1)}ac^{(2)}}\\
		\theta_2 &= K_1^{ac}(ne) = \frac{ac^{(1)}ac^{(2)}(v_1^{(1)}-v_1^{(2)})}{v_1^{(2)}ac^{(1)}-v_1^{(1)}ac^{(2)}}
		\end{align}
	\end{subequations}
	In Equation (\ref{eq:v1_par}), the denominator of the right hand side expression is used to test the identifiability of parameters $V_1^{max}$ (Equation \ref{eq:v1_par}a) and $K_1^{ac}(ne)$ (Equation \ref{eq:v1_par}b) for different available experimental data combinations. Since the enzyme binding constant ($K_1^{ac}(ne)$) and the maximum reaction rate ($V_1^{max}$) cannot be negative, we can further constrain the criteria for identifiability for both these parameters by saying that the evaluated expressions in Equation (\ref{eq:v1_par}) should be non-negative (Figure \ref{fig:ident-flowchart}b).

	We can also apply the proposed methodology to practically identify parameters in $v_1$ under the assumption that the protein concentration for the enzyme \textit{E} is also available, in addition to the measured concentration of the metabolites and fluxes. In doing so, we get two expressions similar to the one shown in Equation (\ref{eq:v1_par}) for $k_1^{cat}$ and $K_1^{ac}$. Here, the value of $V_1^{max}$ in Equation (\ref{eq:flux1a}) above is substituted with $V_1^{max} = k_1^{cat}E$ instead.

	\subsection{Section Title}\label{sec:initial_analysis}
	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=.8\textwidth,height=.6\textheight,keepaspectratio]{figures/figure6/v1_k1cat_v2_v5_2_v3_ck_1_parameter_values}}
		\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux a) $v_1$, b) $v_2$, c) $v_5$, and d)$v_3$. For $v_1$, we have assumed that enzyme concentration is available and have accordingly identified and estimated $k_1^{cat}$, as opposed to $V_1^{max}$. The parameter values for only the second root of $K_e^{fdp}$ in $v_5$ ($K_e^{fdp}(2)$) is shown, since $K_e^{fdp}(1)$ is not estimated by any combination of two experiments, and $V_e^{max}$ is estimated by all combinations. Only one of the two roots for $v_3$ is shown in panel d. The estimated data for the second root has a similar distribution to that of the first root and is shown in the Supplementary Information. Data is generated using the Convenience Kinetic model for allosteric regulation for $v_3$.}\label{fig:ident_values}
	\end{figure}
	\subsection{Relationship between structurally and practically parameter identifiability}\label{sec:proof}
	This section will deal with structural and practical identifiability of parameters in v1, v2, v3 and v5. This section will only focus on the identifiability and not issues related to experimental design. Focus will be on v3 and v5 (which have non-identifiability issues). Also, we could use a better name for this section.	
	\subsection{Parameter non-identifiability due to uncertainty in Experimental Data}\label{sec:uncertainty}
	This will cover issues related to the model used for v3. Convenience kientic model vs MWC model for data generation. Should this uncertainty also include noise?			
	\subsection{A priori experimental design through practical parameter identification}\label{sec:design}	
	Final section talking about distribution of experiments to obtain informative data.

@@

	\clearpage
	\section{Tables, Figures and Figure Captions:}
